The finite representation property for some reducts of relation algebras

### 2021-01-03 frp-paper/Paper.tex
if Heloise has a winning strategy on a countable structure then it's representable

By the condition, $\forall$ makes all witness moves and $\exists$ responds with a witness. Her response is a fresh node $z$ such that $l_{\mathcal{N}_{i + 1}}(x, z) =  \uparrow (l_{\mathcal{N}_i}(x, z) \cup \{ a \})$ and $l_{\mathcal{N}_{i + 1}}(z, y) = \uparrow (l_{\mathcal{N}_i}(z, y) \cup \{ b\})$.

Let us show the following subitems:
\begin{itemize}
  \item $(x, z) \in rep(a)$ ??
  \item $(z, y) \in rep(b)$ ??
\end{itemize}

\end{itemize}
  \end{enumerate}
\end{proof}

>>>>

By the condition, $\forall$ makes the witness moves and $\exists$ responds with a witness. Her response is a fresh node $z$ such that $l_{\mathcal{N}_{i + 1}}(x, z) =  \uparrow (l_{\mathcal{N}_i}(x, z) \cup \{ a \})$ and $l_{\mathcal{N}_{i + 1}}(z, y) = \uparrow (l_{\mathcal{N}_i}(z, y) \cup \{ b\})$. The inclusion $rep(a ; b) \subseteq rep(a) ; rep(b)$ holds since all witness moves have been played and for every such a move there exists a witness.

\item Suppose $(x, y) \in rep(a) ; rep(b)$. We need $(x, y) \in rep(a;b)$. That is, there exists $z \in \mathcal{Nodes}(\mathcal{N})$ with $(x, z) \in rep(a)$ and $(z, y) \in rep(b)$. So, there are $c, d$ such that $c \leq a$ with $c \in l_{\mathcal{N}}(x, z)$ and $d \leq b$ with $d \in l_{\mathcal{N}}(z, y)$.
We also know that $l_{\mathcal{N}}(x, z) ; l_{\mathcal{N}}(z, y) \subseteq l_{\mathcal{N}}(x, y)$ because all composition moves have been played.
So $c ; d \in l_{\mathcal{N}}(x, y)$. That makes $(x, y) \in rep(a;b)$ since $c ; d \leq a ; b$.

\item Injectivity: TODO.
\end{itemize}
  \end{enumerate}
\end{proof}
